Quantifying the ease of viral escape from broad and narrow antibodies to influenza hemagglutinin

### 2017-10-17 paper/manuscript.tex
A few more sentences to results section 4, added methods header

For S139/1, we observed strong escape mutations at sites 156, 158, and 193, in H3 numbering. 
These three sites surround the receptor-binding pocket, and were previously reported as sites of escape in selection experiments with S139/1~\citep{yoshida2009cross}.
The mutation contributing the greatest fraction of virions surviving selection, G158N, introduces a glycosylation motif (N-X-S/T).

% The binding footprint of FI6v3 and C179 and the angle of approach of both antibodies is very similar (cite dreyfus). 
% For these two antibodies, we see selection for a few common escape mutations (S/T at site280, S at site 291, R at 47 / 48 (HA2), but also selection for distinct escape mutations (site 2, site 38, site 323, sites 42, 43)

@@

>>>>

For S139/1, we observed strong escape mutations at sites 156, 158, and 193, in H3 numbering. 
These three sites surround the receptor-binding pocket, and were previously reported as sites of escape in selection experiments with S139/1~\citep{yoshida2009cross}.
The mutation contributing the greatest fraction of virions surviving selection, G158N, introduces a glycosylation motif (N-X-S/T) at this site.

C179 and FI6v3, which share very similar binding footprints and angles of approach~\citep{dreyfus2013structure}, select for identical escape mutations at several sites. Specifically, both antibodies select for mutants K280S and K280T, both of which introduce glycosylation motifs.

% For these two antibodies, we see selection for a few common escape mutations (S/T at site280, S at site 291, R at 47 / 48 (HA2), but also selection for distinct escape mutations (site 2, site 38, site 323, sites 42, 43)

@@

\subsection*{Construction of HA phylogenetic tree}
We downloaded HA sequences from the Influenza Research Database, aligned sequences using MUSCLE... \comment{going to add more here}
